16s taxa stacked bar plot

### 2021-03-08 scripts/49_16s_stacked_barplot.Rmd
great slowly but making progress

# the question is do we go one taxa level higher or make a new color base and shades for the new asv 
```

@@

ggplot(dat,aes(sampleid, count_relative, fill = color_label_group_distinct) ) +
  geom_bar(stat = "identity", position="fill", width = 1) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_blank(),
        legend.position = "none") +
  scale_fill_manual(values = asv_color_set)

@@

ggplot(dat,aes(sampleid, count_relative, fill = color_label_group_distinct) ) +
  geom_bar(stat = "identity", position="fill", width = 1) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_blank(),
        legend.position = "none") +
  scale_fill_manual(values = asv_color_set)
```

>>>>

# so if the genus is unknown then it's gonna be assigned "other" gray color  
# the question is do we go one taxa level higher or make a new color base and shades for the new asv
# after discussing with Tsoni, we decided that it's ok to assign gray to the unknown genus

# merge the new no_color_df_full to the original df
dat <- bind_rows(
  no_color_df_full,
  color_group %>% 
    pluck('FALSE')
)   
```

@@

ggplot(dat,aes(sampleid, count_relative, fill = color_label_group_distinct) ) +
  geom_bar(stat = "identity", position="fill", width = 1) +
  theme_classic() +
  labs(title = 'stacked bar sorted with hclust') +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_blank(),
        legend.position = "none") +
  scale_fill_manual(values = asv_color_set) +
  ggsave('../figs/amplicon/stacked_bar_sorted_with_hclust.pdf', width = 7, height = 5)

@@

ggplot(dat,aes(sampleid, count_relative, fill = color_label_group_distinct) ) +
  geom_bar(stat = "identity", position="fill", width = 1) +
  theme_classic() +
  labs(title = 'stacked bar sorted with hclust and divided to lower and higher diversity') +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_blank(),
        legend.position = "none") +
  scale_fill_manual(values = asv_color_set) +
  ggsave('../figs/amplicon/stacked_bar_sorted_with_hclust_lower_and_higher_diversity.pdf', width = 7, height = 5)
```
